Multi-level modeling with Openflexo/\FML

### 2022-03-25 6-modelpresentation.tex
rewording for placement

This invariant should be completed with additional constraints defined in the
\texttt{Task} concept, which apply to performing actors assigned to enact
tasks.

@@

The used and produced artifacts are implemented by roles
\texttt{usedArtifacts}, \texttt{producedArtifacts} and
\texttt{performingActors} defined in \texttt{Task} (\reqp{13}). An instance
of \texttt{Artifact} specializes \texttt{MultiInstance} and references a set of
\texttt{ArtifactType} through the specialized \texttt{/types} role
(\reqp{14} and \reqp{16}). Likewise, \texttt{Actor} specializes
\texttt{MultiInstance} and references a set of \texttt{ActorType} through the
specialized \texttt{/types} relation (\reqp{15}).

@@

The \texttt{Task} concept delegates this authorization to its task type, as
shown in the following \FML code:

@@

Enforcing those constraints is finally performed by the definition of this
invariant in the \texttt{Task} concept:

>>>>

This invariant should be extended with additional constraints defined in the
\texttt{Task} concept, which apply to actors assigned to enact
tasks.

@@

A \texttt{Task} defines the roles
\texttt{usedArtifacts}, \texttt{producedArtifacts} and
\texttt{performingActors}  (\reqp{13}). An instance
of \texttt{Artifact} specializes \texttt{MultiInstance} and references a set of
\texttt{ArtifactType} through the specialized \texttt{/types} role
(\reqp{14} and \reqp{16}). Likewise, \texttt{Actor} specializes
\texttt{MultiInstance} and references a set of \texttt{ActorType} through the
specialized \texttt{/types} relation (\reqp{15}).

@@

The \texttt{Task} concept delegates this authorization to its task type, as
shown below.

@@

Enforcing those constraints is finally performed by the following
invariant of the \texttt{Task} concept:
